Talks

### 2025-02-04 talks.qmd
update

>>>>

- 4 February: "Do we truly understand those we disagree with, and how could we test this?
The Ideological Turing test", Psychopathology Lab meeting, University of Sheffield (host: Richard Bentall) : [slides](https://docs.google.com/presentation/d/1cEsWXBo4uZFZ8TKJj_NuNGendjLpiC04Wd6DbgmaQP8/edit?usp=sharing)
